\myfont Implementation and evaluation of register allocation used to translate LLVM-{}- to x86-64

### 2024-01-07 article.tex
Nice progress on grapph erxamples

>>>>

If at first a single node of insignificant degree (i.e. \(< 2\)) is selected, it is then removed and pushed to a stack. In Figure \ref{fig:countdown.dot} only \texttt{\%argv} and \texttt{\%c1} are of insignificant degree, so either of those is chosen to be removed (represented with dashed borders and edges).

\begin{figure}[H]
\centering
  \begin{minipage}[b]{0.48\textwidth}
    \begin{subfigure}{0.3\textwidth}
      \includesvg[height=12em]{countdown.simple2}
      \caption{Graph}\label{fig:countdown.dot2}
    \end{subfigure}
\hfill
    \begin{subfigure}{0.18\textwidth}
      \texttt{\%c1}
      \caption{Stack}
      \label{fig:second}
    \end{subfigure}
   \end{minipage}
  \begin{minipage}[b]{0.48\textwidth}
    \begin{subfigure}{0.3\textwidth}
      \includesvg[height=12em]{countdown.simple2}
      \caption{Graph}\label{fig:countdown.dot2}
    \end{subfigure}
\hfill
    \begin{subfigure}{0.18\textwidth}
      \texttt{\%c1}
      \caption{Stack}
      \label{fig:second}
    \end{subfigure}
   \end{minipage}
\end{figure}
